Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-05-22 Paper Sigatoka - 2015.tex
Removing to-do's and check-me's and some minor issues

\modulolinenumbers[5]

@@

\TODO{ CORREGIDO (LUIS-ALEX)
revisar si la nueva redacción de este párrafo coincide con la
  original.  Eso es lo que creo se quería decir, porque no quedaba
  claro cuál sistema fue creado por quién...  Las referencias a cada
  sistema en algo así son absolutamente necesarias.  Favor reemplazar
   por las referencias correspondientes (Pablo, 1/5/16)}

The early warning system developed by Ganry and Meyer \citep{ganry1972} and modified by Ganry and Laville \citep{ganry1983} to use for controlling yellow Sigatoka in Cameroon, later was adapted for Ternesien \citep{Ternesien1985} and Fouré \citep{foure1988} for the black Sigatoka.

This bilogical warning system is based on weekly quantified observations of the disease progression on young leaves of the plant, according to
Fouré's scale of the symptom stages. The numeric coefficients describe the degree of incidence and the severity of the disease development.  These coefficients are used to
calculate two variables: gross sum and state of evolution.

\TODO{ EN REALIDAD ASÍ ES USADO EN EL TEXTO FUENTE EN INGLÉS (LUIS ALEX)
coefficients??  No suena como coeficientes (un factor que
  multiplica términos en una función) sino como una calificación o
  nota o algo así (quizá ``grade''?).  ``Arbitrary coefficient'' no
  tiene sentido por el ``arbitrary''... No creo que sean tan
  arbitrarios sino predefinidos.  De hecho, el párrafo que sigue dice
  que suben con el avance de síntomas, es decir, no es tan
  ``arbitrario''.  Quizá querés decir ``arbitrarily chosen''?.  No
  estoy seguro si entiendo lo que se quiere decir aquí.}

The gross sum is based on the present disease progression stage and 
\instead{an arbitrary coefficients}{the arbitrarily chosen grading},
which increases with the advance of the symptoms and the
juvenility of the leaf.
%
The state of evolution is calculated using the gross sum and the
foliar emission period.
%
Although threshold levels were initially suggested as a guide to spray
\instead{timing}{schedules}, the fluctuation of these two variables
was found to better define appropiate times to spray
\citep{Marinetal2003}.

In Costa Rica the black Sigatoka is frequently treated with
chemical fungicides.
%
Depending on the zone of production and the weather conditions,
45--55~cycles/year of fungicide applications are required to keep this
disease under control and to produce the expected fruit quality for the
international markets.
%
This represent a cost per hectare per year in the range between US\$1600 and
US\$2000; about 0.64--0.80 cents of the production costs for a
18.14\,kg box.
%
Overall, this represents 10\%--12\% of the total production costs.

The past and present rates of disease development can in principle be used
to predict its future behavior and to determine whether
a particular fungicide spray program will be able to effectively and
economically control the disease \citep{ChuangJeger1987}.

@@

The outline of the paper is as follows. In Section 2, we introduce the machine learning techniques used in this research and the main related works. In section 3, we present the data used and the methodology for the study results. In section 4, we present the results and their discussion. Our conclusions and future work are presented in Section 5.

\section{Machine learning techniques and Related works}
In this section we summary the machine learning techniques used and we present the main related works.

@@

\section{Specification of data and methodology}
In this section, we present the data and how we worked to obtain our results.

@@

\section{Results and discussion}

@@

\section{Future work}

>>>>

\modulolinenumbers[1]

@@

The early warning system developed by Ganry and Meyer
\citep{ganry1972} and modified by Ganry and Laville \citep{ganry1983}
to control yellow Sigatoka in Cameroon, was later adapted by
Ternesien \citep{Ternesien1985} and Fouré \citep{foure1988} for the
black Sigatoka.

This bilogical warning system is based on weekly quantified
observations of the disease progression on young leaves of the plant,
according to Fouré's scale of the symptom stages.
%
The numeric coefficients describe the degree of incidence and the
severity of the disease development.  These coefficients are used to
calculate two variables: gross sum and state of evolution.

The gross sum is based on the present disease progression stage and
the numeric coefficients, which increases with the progression of
the symptoms and the juvenility of the leaf.
%
The state of evolution is calculated using the gross sum and the
foliar emission period.
%
Although threshold levels were initially suggested as a guide to spray
schedules, the fluctuation of these two variables
was found to better define appropiate times to spray
\citep{Marinetal2003}.

In Costa Rica the black Sigatoka is frequently treated with
chemical fungicides.
%
Depending on the zone of production and the weather conditions,
45--55~cycles/year of fungicide applications are required to keep this
disease under control and to produce the expected fruit quality for the
international markets.
%
This represents a cost per hectare per year in the range between US\$1600 and
US\$2000; about 0.64--0.80 cents of the production costs for a
18.14\,kg box.
%
Overall, this represents 10\%--12\% of the total production costs.

The past and present rates of disease development can in principle be used
to predict its future behavior and to determine whether
a particular fungicide spray program will be able to effectively and
economically control the disease \citep{ChuangJeger1987} or not.

@@

The outline of the paper is as follows: in Section~\ref{sec:techs}, we
introduce the machine learning techniques used in this research and
the main related works. Section~\ref{sec:data} summarizes the data the
methodology used in this study.  The results and their discussion are
presented in section~\ref{sec:results}.  We present the main
conclusions and lines for future works in Section~\ref{sec:concl}.

\section{Machine learning techniques and Related works}
\label{sec:techs}

In this section we summary the machine learning techniques used and we present the main related works.

@@

\section{Specification of data and methodology}
\label{sec:data}

In this section, we present the data and how we worked to obtain our results.

@@

\section{Results and discussion}
\label{sec:results}

@@

\section{Conclusions}
\label{sec:concl}

\subsection{Future work}
